Vibronic coupling in C$_2$H: implications for astrochemistry

### 2022-03-20 Aug2021-CH2-.tex
update

\begin{align}
H &= T_n1+V\\
V &= \bordermatrix{ & X & A(a') & A(a'') \cr
	X &\substack{\Delta_0^X+F_1^Xq_1+F_3^Xq_3+\\ 
		\frac{1}{2} \sum_{ij}F^X_{ij}q_iq_j}& \lambda q_{3a} & \lambda q_{3b} \cr
	A(a') & \lambda q_{3a} & \substack{\Delta^A_0+F^A_1q_1+F^A_3q_3\\+\frac{1}{2}\sum_{ij}F^A_{ij}q_iq_j+\\\frac{1}{2}\eta(q_{3a}^2-q_{3b}^2)} & \eta q_{3a}q_{3b} \cr
	A(a'') & \lambda q_{3b} & \eta q_{3a}q_{3b} & \substack{\Delta_0^A+F_1^Aq_1+F_3^Aq_3\\+\frac{1}{2}\sum_{ij}F_{ij}^Aq_iq_j\\-\frac{1}{2}\eta(q_{3a}^2-q_{3b}^2) } } \qquad
\label{eq:calc1}
\end{align}

where the summations run over the dimensionless normal modes ($q_i$) that serve as the coordinate system for the problem.   For convenience, the latter are chosen to be those of the anion, which considerably facilitates calculation of the spectral intensities.  In Eq.~(\ref{eq:calc1}), the diagonal terms of V (excluding those that carry the Renner-Teller coupling constant $\eta$) represent the quasidiabatic potential energy surfaces of the $\Sigma$, and the two components of the $\Pi$ state, chosen here as those in which the unpaired electron lies within or is perpendicular to an arbitrarily chosen plane, designated as A(a$'$) and A(a$''$), respectively. $\Delta_0^X$ is the separation of the anion and $\Sigma$ states at the origin of the coordinate system (the vertical electron detachment energy), and $\Delta_0^{\Pi}$ is the gap between anion and $\Pi$ states at the same geometry.

@@

\begin{align}
F_{33}^X &= f_{33}^X+\frac{2\lambda^2}{(\Delta_0^A-\Delta_0^X)}\\
F_{33}^A &= f_{3a3a}^{A(a')}-\frac{2\lambda^2}{(\Delta_0^A-\Delta_0^X)}-\eta
\label{eq:calc2}
\end{align}

@@

\begin{equation}
\eta = \frac{1}{2}\left[ f_{3a3a}^{A(a')}-f_{3b3b}^{A(a')}-\frac{2\lambda^2}{(\Delta_0^A-\Delta_0^X)}\right]
\label{eq:calc3}
\end{equation}

@@

% Create the reference section using BibTeX: 
\bibliography{C2H.bib}

>>>>

\begin{align}
H &= T_n1+V\\
V &= \bordermatrix{ & X & A(a') & A(a'') \cr
	X &\substack{\Delta_0^X+F_1^Xq_1+F_3^Xq_3+\\ 
		\frac{1}{2} \sum_{ij}F^X_{ij}q_iq_j}& \lambda q_{2a} & \lambda q_{2b} \cr
	A(a') & \lambda q_{2a} & \substack{\Delta^A_0+F^A_1q_1+F^A_3q_3\\+\frac{1}{2}\sum_{ij}F^A_{ij}q_iq_j+\\\frac{1}{2}\eta(q_{2a}^2-q_{2b}^2)} & \eta q_{2a}q_{2b} \cr
	A(a'') & \lambda q_{2b} & \eta q_{2a}q_{2b} & \substack{\Delta_0^A+F_1^Aq_1+F_3^Aq_3\\+\frac{1}{2}\sum_{ij}F_{ij}^Aq_iq_j\\-\frac{1}{2}\eta(q_{2a}^2-q_{2b}^2) } } \qquad
\label{eq:calc1}
\end{align}

where the summations run over the dimensionless normal modes ($q_i$) that serve as the coordinate system for the problem.   For convenience, the latter are chosen to be those of the anion, which considerably facilitates calculation of the spectral intensities.  In Eq.~(\ref{eq:calc1}), the diagonal terms of V (excluding those that carry the Renner-Teller coupling constant $\eta$) represent the quasidiabatic potential energy surfaces of the $\Sigma$, and the two components of the $\Pi$ state, chosen here as those in which the unpaired electron lies within or is perpendicular to an arbitrarily chosen plane, designated as A(a$'$) and A(a$''$), respectively. $\Delta_0^X$ is the separation of the anion and $\Sigma$ states at the origin of the coordinate system (the vertical electron detachment energy), and $\Delta_0^{A}$ is the gap between anion and $\Pi$ states at the same geometry.

@@

\begin{align}
F_{22}^X &= f_{22}^X+\frac{2\lambda^2}{(\Delta_0^A-\Delta_0^X)}\\
F_{22}^A &= f_{2a2a}^{A(a')}-\frac{2\lambda^2}{(\Delta_0^A-\Delta_0^X)}-\eta
\label{eq:calc2}
\end{align}

@@

\begin{equation}
\eta = \frac{1}{2}\left[ f_{2a2a}^{A(a')}-f_{2b2b}^{A(a')}-\frac{2\lambda^2}{(\Delta_0^A-\Delta_0^X)}\right]
\label{eq:calc3}
\end{equation}

@@

% Create the reference section using BibTeX: 
\bibliography{2022C2H.bib}
